Spatial Analysis

### 2021-06-29 Scripts/spatial_analisis.Rmd
created figure of buffers for manuscript

land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
  filter(ID %in% States) %>%

@@

@@

>>>>

land_sf <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
  filter(ID %in% States) %>% 
  mutate(abrev = c("CO","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VI"))

@@

```{r cropped_plot_paper}

plot_data <-grid_eez_sf %>% 
    mutate(state = str_to_sentence(state)) %>% 
    left_join(state_lat)

p <- gridExtra::grid.arrange(
  # Overall (overlapping) position
  ggplot(plot_data) +
    geom_sf(data = eez_sf, aes(), fill = "white") + 
    geom_sf(aes(color = order, fill = order), alpha = 0.3) +
    geom_sf(data = land_sf, aes()) +
    geom_sf_label_repel(data = land_sf, aes(label= abrev), 
                      size = 2,
                      box.padding = 0.10,
                      hjust = 1) +
    scale_color_manual(values = state_pallet) +
    scale_fill_manual(values = state_pallet) +
    my_ggtheme_p(leg_pos = "",
                 ax_tx_s = 12) +
    coord_sf(ylim = c(30,48)) +
    scale_y_continuous(breaks = c(30,35,40,45))+
    labs(x = "", y = ""),
  # Showing each state separately

    ggplot(plot_data) +
    geom_sf(data = land_sf, aes(), fill = "grey80") +
    geom_sf( aes(color = order),size = 0.1, alpha = 0.8) +
    facet_wrap(~ state) +
    theme(legend.position = "top") +
    scale_color_manual(values = state_pallet,
                       labels = plot_data %>% arrange(order) %>%  pull(state) %>% unique()) +
    my_ggtheme_p(leg_pos = "",
                 ax_tx_s = 6,
                 axx_tx_ang = 45,
                 hjust = 1
                 ),
  nrow = 1,
  bottom = "Longitude",
  left = "Latitude")

  ggsave(filename = "buffer_figure.jpg",
         plot = p,
         path = my_path("R","Figures"),
         width = 10,
         height = 5
         )

@@

# Managed species by Mid-Atlantic Council Management Plans, and State waters
# https://www.fisheries.noaa.gov/new-england-mid-atlantic/commercial-fishing/new-england-mid-atlantic-fishery-management-plans

Species <- c(
  "Scomber scombrus",
  "Doryteuthis (Amerigo) pealeii", #longfin squid
  "Peprilus triacanthus", # butterfish
  "Illex illecebrosus", #shortfin squid
  "Paralichthys dentatus", #summer flounder
  "Stenotomus chrysops", #Scoop"
  "Centropristis striata", # black sea bass
  "Pomatomus saltatrix", # Bluefish
  "Lopholatilus chamaeleonticeps", #golden tilefish
  "Caulolatilus microps", #blueline tilefish
  "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)

  )
